\documentclass{resume}
\usepackage{lmodern}
\usepackage{fontawesome}

\begin{document}
\fontspec{Lato}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{}{Xiaomin Liu}
{\href{https://linkedin.com/in/xiaomin-liu-liu}{linkedin.com/in/xiaomin-liu-liu}}
{\href{mailto:xl4624@nyu.edu}{xl4624@nyu.edu}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{New York University} \positiondate{\textit{May 2026}} \\
\fontsize{10.5pt}{12pt}\selectfont
\textbf{Bachelor of Arts}, Computer Science, \textbf{Minor} in Mathematics \hfill 
\textbf{GPA:} 3.84 \\
\hspace*{8.5mm}\textbf{Honors:} Presidential Honors Scholars Program (Top 10\%) | CAS Scholarship (full-ride) \\
\hspace*{8.5mm}\textbf{Activities:} BUGS@NYU EBoard Member | Tech@NYU Tech Trek Mentor \\
\hspace*{8.5mm}\textbf{Relevant Coursework:} Data Structures | Basic Algorithms | Data Management and Analysis (currently taking)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\subsection{Niantic}- Incoming Software Engineering Intern \positiondate{May 2024}

\subsection{BUGS@NYU}- Software Developer \positiondate{Jan 2024 - Present} \\
\begin{tightemize}
    \item Collaborating with a team of 6 to develop a Leetcode Multiplayer open-source platform this semester.
\end{tightemize}

\subsection{Vantage}- Software Engineering Intern \positiondate{July 2023 - Oct 2023} \\
\technologies{Ruby, Ruby on Rails, JavaScript, HTML, PostgreSQL, Azure, Temporal, Sentry} \\
\begin{tightemize}
    \item Launched \href{https://www.vantage.sh/blog/vantage-launches-azure-active-resources}{\underline{Azure Active Resources}}, a tracking and reporting of Azure resource utilization and costs feature that enables users to filter their Azure spending by resource metadata.
    \item Designed and built a daily Temporal workflow that asynchronously updates \textasciitilde100,000 records for over 6,500 users by leveraging Azure's REST APIs to fetch data from more than 30 different Azure services.
    \item Integrated a line graph using HTML and JavaScript to display aggregated related resource costs in 30 day periods.
    \item Minimized issues reported by Sentry logs by writing and maintaining 40 unit tests and documented how to add new Azure services for future developers.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section
[\href{http://github.com/xl4624}{\raisebox{.4mm}{[github.com/xl4624]\hspace{3mm}}}]
{Projects}

\subsection{Chess with Friends}\href{https://github.com/xl4624/chess-with-friends}{\fontsize{14pt}{14pt}\selectfont\faGithub} \\
\technologies{Python, Flask, JavaScript, PostgreSQL, HTML, CSS, Docker} \\
\begin{tightemize}
    \item Spearheaded a team of 3 to develop an online Multiplayer chess web application using Flask and Socket.IO to handle asynchronous communication between the server and clients.
    \item Implemented real-time chessboard updates, a chat feature, and a move history table in JavaScript and HTML.
    \item Directed project management efforts by delegating tasks among team members, conducting code reviews, and thoroughly documenting/testing the codebase.
\end{tightemize}

\subsection{Debugging Memory Allocator} \\
\technologies{C++} \\
\begin{tightemize}
    \item Created a custom memory allocator using C++ that supports malloc, free, and realloc functions, capturing memory leaks and buffer overflows.
    \item Utilized a linear, sorted free list to manage free memory blocks and implemented methods for splitting and coalescing blocks using pointer arithmetic.
\end{tightemize}

\subsection{sudo ku}\href{https://github.com/xl4624/sudo-ku}{\fontsize{14pt}{14pt}\selectfont\faGithub} \\
\technologies{Go, JSON, HTTP} \\
\begin{tightemize}
    \item Built a CLI web scraper that fetches and parses the latest Sudoku puzzles from \href{https://www.sudoku.au}{\underline{sudoku.au}} and solves them using a depth-first search backtracking algorithm.
\end{tightemize}

\subsection{COVID-19 Visualization}\href{https://github.com/xl4624/covid-visualization}{\fontsize{14pt}{14pt}\selectfont\faGithub} \\
\technologies{Python, pandas, Matplotlib} \\
\begin{tightemize}
    \item Analyzed and visualized COVID-19 data from the CDC COVID Data Tracker using pandas and matplotlib to create a choropleth map to track the number of cases and deaths in the US.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}

\fontsize{10.5pt}{12pt}\selectfont
\vspace{-1mm}
\textbf{Languages:}\hspace{1mm} Python, Java, C++, JavaScript/TypeScript, Ruby, HTML, Lua, SQL, CSS, Bash \\
\textbf{Frameworks and Libraries:}\hspace{1mm} Ruby on Rails, React, Flask, Django, pandas, NumPy, Matplotlib, Node.js, Express \\
\textbf{Technologies:}\hspace{1mm} Git, Unix, Docker, Azure, AWS(EC2, RDS), Sentry, Temporal, Postman, Vim

\end{document}
